\pkg{ggenealogy}: An \proglang{R} Package for Visualizing Genealogical Data

### 2016-11-22 article.tex
ReplicationScript testing

\begin{Code}
plotPath(pathTN, sbGeneal, "devYear")
\end{Code}

@@

\begin{Code}
R> pathBZ <- getPath("Bedford", "Zane", sbIG, sbGeneal, "devYear")
R> plotPath(pathBZ, sbGeneal, "devYear", fontFace = 2) +
+    ggplot2::xlab("Development Year")
\end{Code}

@@

\begin{Code}
>R varieties <- c("Brim", "Bedford", "Calland", "Dillon", "Hood", "Narow",
+    "Pella", "Tokyo", "Young", "Zane")
>R plotDegMatrix(varieties, sbIG, sbGeneal, "devYear") +
+    ggplot2::scale_fill_continuous(low = "white", high = "darkgreen") +
+    ggplot2::theme(legend.title = ggplot2::element_text(size = 15),
+    legend.text = ggplot2::element_text(size = 15)) +
+    ggplot2::labs(x = "Variety", y = "Variety")
\end{Code}

@@

\begin{CodeChunk}
\begin{CodeInput}
R> statIG <- dfToIG(statGeneal)
R> pathCB <- getPath("David Cox", "Petra Buzkova", statIG, statGeneal,
+    "gradYear", isDirected = FALSE)
R> plotPath(pathCB, "gradYear", fontFace = 4) + ggplot2::xlab("Graduation
+    Year") + ggplot2::theme(axis.text = ggplot2::element_text(size = 10),
+    axis.title = ggplot2::element_text(size = 10)) +
+    ggplot2::scale_x_continuous(expand = c(.1, .2))
\end{CodeInput}
\end{CodeChunk}

@@

\begin{CodeChunk}
\begin{CodeInput}
R> plotPathOnAll(pathCB, statGeneal, statIG, "gradYear", bin = 200)
+    ggplot2::theme(axis.text = ggplot2::element_text(size = 8), axis.title =
+    ggplot2::element_text(size = 8)) + ggplot2::scale_x_continuous
+    (expand = c(.1, .2)) + ggplot2::xlab("Graduation Year")
\end{CodeInput}
\end{CodeChunk}

@@

We would like to state that users can still hard code one or two variables in the \code{plotPathOnAll()} function, even with the \code{animate} option set to a value of ``TRUE". The first call to the \code{plotPathOnAll()} function below would produce an interactive plot with the yield on the horizontal axis. When hovering over labels, the label name and yield value is revealed. The second call to the \code{plotPathOnAll()} function below would produce an interactive plot with the yield on the horizontal axis and development year on the vertical axis. When hovering over labels, the label name, yield value, and development year is revealed.

@@

\begin{CodeChunk}
\begin{CodeInput}
R> AKBranchYield <- getBranchQuant("A.K.", sbGeneal, "yield", 15)
R> select(AKBranchYield,-DesNames)
\end{CodeInput}
\begin{CodeOutput}
           Name     Mean       SD Count NACount
1 A.K. (Harrow) 2932.154 197.0092    54      41
2        Illini 2856.667 210.7801   131     125
\end{CodeOutput}
\end{CodeChunk}

@@

\begin{CodeChunk}
\begin{CodeInput}
R> CoxBranchYear <- getBranchQuant("David Cox", statGeneal, "gradYear", 15)
R> head(select(CoxBranchYear,-DesNames),10)
\end{CodeInput}
\begin{CodeOutput}
                         Name     Mean        SD Count NACount
1                 Mark Berman 2007.200  6.340347     5       0
2                  Henry Wynn 2005.333  7.637626     3       0
3                Rodney Wolff 2003.500  2.121320     2       0
4                 Jane Hutton 2003.000        NA     1       0
5              Gauss Cordeiro 2002.643  7.722167    14       0
6             Peter McCullagh 2001.231  8.778645    26       0
7             Basilio Pereira 2000.647 10.074356    17       0
8            Peter Bloomfield 1999.918 11.707969    49       0
9            Adelchi Azzalini      NaN        NA     0       0
10 Amy Berrington de Gonzales      NaN        NA     0       0
\end{CodeOutput}
\end{CodeChunk}

>>>>

\begin{Code}
R> plotPath(pathTN, sbGeneal, "devYear")
\end{Code}

@@

\begin{Code}
R> pathBZ <- getPath("Bedford", "Zane", sbIG, sbGeneal, "devYear")
R> plotPath(pathBZ, sbGeneal, "devYear", fontFace = 2) + ggplot2::xlab
+    ("Development Year")
\end{Code}

@@

\begin{Code}
>R varieties <- c("Brim", "Bedford", "Calland", "Dillon", "Hood", "Narow",
+    "Pella", "Tokyo", "Young", "Zane")
>R plotDegMatrix(varieties, sbIG, sbGeneal) +
+    ggplot2::scale_fill_continuous(low = "white", high = "darkgreen") +
+    ggplot2::theme(legend.title = ggplot2::element_text(size = 15),
+    legend.text = ggplot2::element_text(size = 15)) + ggplot2::labs(x = 
+    "Variety", y = "Variety")
\end{Code}

@@

\begin{CodeChunk}
\begin{CodeInput}
R> statIG <- dfToIG(statGeneal)
R> pathCB <- getPath("David Cox", "Petra Buzkova", statIG, statGeneal,
+    "gradYear", isDirected = FALSE)
R> plotPath(pathCB, statGeneal, "gradYear", fontFace = 4) +
+    ggplot2::xlab("Graduation Year") + ggplot2::theme(axis.text = 
+    ggplot2::element_text(size = 10), axis.title = ggplot2::element_text(
+    (size = 10)) + ggplot2::scale_x_continuous(expand = c(.1, .2))
\end{CodeInput}
\end{CodeChunk}

@@

\begin{CodeChunk}
\begin{CodeInput}
R> plotPathOnAll(pathCB, statGeneal, statIG, "gradYear", bin = 200) +
+    ggplot2::theme(axis.text = ggplot2::element_text(size = 8), axis.title =
+    ggplot2::element_text(size = 8)) + ggplot2::scale_x_continuous
+    (expand = c(.1, .2)) + ggplot2::xlab("Graduation Year")
\end{CodeInput}
\end{CodeChunk}

@@

We would like to state that users can still hard code one or two variables in the \code{plotPathOnAll()} function, even with the \code{animate} option set to a value of ``TRUE". The first call to the \code{plotPathOnAll()} function below would produce an interactive plot with the yield on the horizontal axis. When hovering over labels, the label name and yield value would be revealed. The second call to the \code{plotPathOnAll()} function below would produce an interactive plot with the yield on the horizontal axis and development year on the vertical axis. When hovering over labels, the label name, yield value, and development year would be revealed. We do not include the animated videos that the below code creates in this document, but readers can use the below code to create them on their own.

@@

\begin{CodeChunk}
\begin{CodeInput}
R> AKBranchYield <- getBranchQuant("A.K.", sbGeneal, "yield", 15)
R> select(AKBranchYield, -DesNames)
\end{CodeInput}
\begin{CodeOutput}
           Name     Mean       SD Count NACount
1 A.K. (Harrow) 2932.154 197.0092    54      41
2        Illini 2856.667 210.7801   131     125
\end{CodeOutput}
\end{CodeChunk}

@@

\begin{CodeChunk}
\begin{CodeInput}
R> CoxBranchYear <- getBranchQuant("David Cox", statGeneal, "gradYear", 15)
R> head(select(CoxBranchYear, -DesNames), 10)
\end{CodeInput}
\begin{CodeOutput}
                         Name     Mean        SD Count NACount
1                 Mark Berman 2007.200  6.340347     5       0
2                  Henry Wynn 2005.333  7.637626     3       0
3                Rodney Wolff 2003.500  2.121320     2       0
4                 Jane Hutton 2003.000        NA     1       0
5              Gauss Cordeiro 2002.643  7.722167    14       0
6             Peter McCullagh 2001.231  8.778645    26       0
7             Basilio Pereira 2000.647 10.074356    17       0
8            Peter Bloomfield 1999.918 11.707969    49       0
9            Adelchi Azzalini      NaN        NA     0       0
10 Amy Berrington de Gonzales      NaN        NA     0       0
\end{CodeOutput}
\end{CodeChunk}
